---
title: "README"
format: gfm
editor: visual
---

## lotoseurosR

Tools to aid inputs and outputs for the LOTOS-EUROS (LE) chemical transport model https://lotos-euros.tno.nl/open-source-version/

The model has been downloaded and run on the default settings, with the outputs in the mod_files/outputs folder. Cloning this folder and running the functions should work with the model files. The functions should also work with any LE model ooutput files provided the output files are given distinguishable names that can be given to the pattern input to the function.

The input_concs and input_meteo will import the concentration outputs and output as a dataframe that can be used with openair and saqgetr to validate.

By converting to georeferenced raster layers and raster bricks simplifies processing and plotting

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
